Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/paper.tex
update definition, not too great and a bit circular

This hint can be used to mark functions as \emph{invariant}. A function is
termed invariant if, during the execution of the program, successive calls to
the function with identical arguments always return the same result. From this
definition follows that a call to an invariant function with constant arguments
in a trace can be replaced with the result of the call.

>>>>

XXX not too happy with the definition

This hint can be used to mark functions as \emph{invariant}. A function is
termed invariant if, during the execution of the program, the results of
subsequent calls to the function with identical arguments may be be replaced
with the result of the first call without changing the program's behaviour.
From this
definition follows that a call to an invariant function with constant arguments
in a trace can be replaced with the result of the call.\footnote{This property
is less strict than that of a "pure" function, because it is only about actual
calls during execution.}
